The goal of this thesis was to establish a practically applicable framework for describing the electromagnetic coupling between electrically small antennas and TEM cells. Modern electronic systems are increasingly compact and operate at higher frequencies, giving rise to small conducting structures that are sources of unintentional radiation and that couple to their environment. This coupling can cause significant electromagnetic compatibility issues. 

TEM cells provide a standardized measurement environment for characterizing such emissions, and therefore serve as the primarily used environment for these investigations. To characterize the coupling behavior of electrically small antennas within TEM cells, this thesis aims to represent their electromagnetic emissions through equivalent electric and magnetic dipole moments. They serve as accurate equivalent models that not only substantially reduce computational effort compared to simulating the full antenna structure, but also reveal the underlying physical mechanisms driving the electric and magnetic coupling to the TEM cell.

Building upon this dipole-moment framework, this thesis presents investigations of the shielding behavior of electrically small antennas enclosed by various shielding materials. By combining the coupling framework developed for TEM cells with an analysis of shielding effectiveness, this thesis derives direct relations between the dominant near-field character of an antenna, as characterized by its equivalent dipole moments, and the shielding performance of a given material. Together, these two interconnected frameworks provide a theoretical and numerical basis for analyzing the radiation and shielding behavior of electrically small antennas in TEM cells, and contribute toward EMC-aware electronic design.

The framework for describing the coupling mechanisms between electrically small antennas and the TEM cell is constructed by applying the Lorentz reciprocity theorem, which relates an arbitrary current source inside the TEM cell to the modal coefficients of the fields propagating toward the output ports. The total fields in the TEM cell are expressed as a superposition of propagating modes, each weighted by a corresponding modal coefficient. The formulation for the radiated fields of the arbitrary current source is specialized for dipole moments, and further for electrically small antennas, yielding expressions describing the radiation of both. This framework then associates the displacement currents of the electrically small antennas with the electric dipole moment, and the TEM cell magnetic coupling with the magnetic dipole moment. For the dominant TEM mode, these two mechanisms produce a measurable phase difference between the two output port signals, enabling the separate determination of the electric and magnetic dipole moments.

The numerical investigations validate the theoretical framework developed in this thesis across a range of antenna geometries. For the monopole antenna, the equivalent electric dipole moment increases linearly with frequency while the magnetic dipole moment remains negligible throughout the investigated frequency range. This behaviour is directly explained by the feedpoint quantities: the approximately constant voltage and linearly increasing displacement current drive the electric coupling to the septum, as expressed through the constructed framework. The loop antenna, by contrast, generates a dominant magnetic dipole moment whose magnitude grows approximately linearly at low frequencies ($\propto f$) and transitions to a slower growth rate ($\propto \sqrt{f}$) at higher frequencies, alongside a growing electric dipole moment arising from the increasing displacement currents between the antenna conductor and the septum. The output powers attributed to the equivalent dipole moments agree with those of the full antenna simulations, confirming the validity of the dipole model for the investigated antennas.

The three additional antenna structures examined, namely the loop antenna with gap, the inverted-F antenna, and the center-fed monopole, demonstrate that geometrical modifications of a reference antenna change the equivalent electric and magnetic dipole moments in a predictable manner. Introducing a gap into the return path of the loop antenna reduces the conduction current and correspondingly weakens the magnetic dipole moment, while enhancing the electric dipole moment through increased charge accumulation and displacement currents at the gap boundaries. Adding a linear arm to the loop geometry increases the charge distribution along the arm, thereby strengthening the electric dipole moment contribution. In each case, the equivalent dipole moments closely reproduce the output power of the full antenna models, which supports the applicability of the framework to a wide variety of electrically small radiating structures.

The equivalent circuit models for the monopole and loop antennas express the coupling mechanisms in terms of lumped parameters. The coupling capacitance $C_k$ represents the displacement current path that drives the electric dipole moment, while the mutual inductances $M_{A,T1}$ and $M_{A,T2}$ model the magnetically induced voltage across the TEM cell that gives rise to the magnetic dipole moment. For the monopole antenna, the mutual inductances are found to be negligible and the coupling is driven entirely by $C_k$, while for the loop antenna both mechanisms contribute. The dipole moments derived from these circuits quantitatively agree with the FEM results.
% at higher frequencies, with increasing deviations at lower frequencies attributed to the sensitivity of the extracted lumped parameters to numerical inaccuracies in the near-field region.

The shielding investigations demonstrate that the near-field character of an antenna, as characterized by its equivalent dipole moments, directly determines which shielding material provides effective attenuation. The analysis is interpreted through an impedance mismatch framework which, while strictly derived for incident plane waves, provides a consistent physical explanation for the observed near-field shielding behavior. 

Materials with high permittivity, such as barium titanate, possess a low intrinsic wave impedance, creating a large impedance mismatch with the high source-field impedance of electric near-fields, and thereby achieving high electric shielding effectiveness. Conversely, this low intrinsic impedance reduces the mismatch with the low source-field impedance of magnetic near-fields, which explains the poor and even negative magnetic shielding effectiveness observed. Ferrite, with its high permeability, raises its intrinsic wave impedance, producing a large mismatch with low-impedance magnetic near-field sources and thereby achieving effective magnetic shielding. Silver achieves the highest overall shielding effectiveness among the materials investigated. Its very low material wave impedance yields a strong impedance mismatch with high-impedance electric near-field sources, while the magnetic shielding effectiveness increases with frequency as absorption grows with decreasing skin depth. By contrast, the electric shielding effectiveness begins to decline at higher frequencies as the rising material wave impedance reduces the impedance mismatch with electric near-field sources. These behaviors are confirmed by simulations of antennas in shielding enclosures, where barium titanate reduces the emission of the monopole antenna and ferrite attenuates that of the loop antenna, consistent with their respective near-field characters.

Replacing the full antenna models with their equivalent dipole moments inside shielding enclosures yields accurate results when the shielding material is relatively transparent to the dominant near-field of the enclosed antenna, but accuracy decreases as shielding effectiveness increases. This limitation arises because the dipole model treats the source as an impressed quantity, neglecting the interaction between the antenna and its shielding environment.

Several directions for future work arise from these findings. The equivalent circuit models could be extended to include higher-order modes, providing a more complete analytical description of the antenna to TEM cell coupling beyond the usable single-mode frequency range. The accuracy of the dipole approximation within shielding enclosures could be improved by introducing correction factors of the propagating modal fields in the Lorentz reciprocity theorem applied in this framework. Finally, extending the analysis to electrically larger antenna configurations in which multiple dipole moment components are simultaneously active, or in which higher-order TEM cell modes are deliberately utilized, offers a promising direction toward a more complete characterization of radiating structures in EMC testing environments.
