% !TeX root = Documentation.tex

In recent years, electronic systems have demonstrated a clear trend toward reduced physical dimensions and increased operating speeds. As a result, small conducting structures carrying high-frequency currents become significant unintentional radiators, behaving as antennas and coupling to their surroundings in ways that can compromise electromagnetic compatibility (EMC). Addressing EMC at the design stage reduces the risk of costly redesigns and ensures limited emissions and reliable operation in the presence of external interference  \cite[p.~64]{Paul_Scully_Steffka_2023}.

TEM cells are a widely adopted tool for characterizing electromagnetic emissions from small devices under approximately free-space conditions. Their well-defined modal fields make them suitable for coupling analyses, and they have been extensively used in standardized emissions testing \cites{9153508,809846,Koepke_1989}. Understanding how a device couples to a TEM cell is therefore of direct practical relevance for EMC.

For electrically small antennas and devices, the emitted fields can be accurately represented through equivalent electric and magnetic dipole moments. The framework constructed in this thesis associates the electric dipole moment with the displacement currents of the antenna coupling to the TEM cell, while the magnetic dipole moment reflects the antenna's inductive coupling driven by conduction current. Prior work has used similar frameworks to analyze the coupling between small antennas and TEM cells \cites{Kreindl_Bauernfeind_Weiss_Stockreiter_Kaltenbacher_2024,10742020,10274360,Sreenivasiah_Chang_Ma_1981}, with dipole moments determined either through measurements or through numerical approaches. However, measurements introduce uncertainties owing to the test setup, and no comprehensive numerical framework has yet unified these connections systematically across a range of antenna geometries.

This thesis addresses this gap by developing a comprehensive numerical framework, that systematically derives the equivalent electric and magnetic dipole moments of electrically small antennas and connects them to their coupling behavior within TEM cells. Using the finite element method implemented in Ansys HFSS, this thesis simulates antenna geometries, thereby avoiding inaccuracies inherent in physical measurement setups. The theoretical framework builds on a decomposition of the propagating fields in the TEM cell into modes, in which the total field is expressed as a superposition of mode fields weighted by modal coefficients. Applying the Lorentz reciprocity theorem then relates arbitrary current sources inside the TEM cell directly to these coefficients, enabling the coupling of any source to each propagating mode to be determined. Applying this formulation to electric and magnetic dipole moments, and further to electrically small antennas, yields expressions describing their radiation inside the TEM cell.

The results derived in this thesis can be categorized in three main findings: First, it derives and validates the equivalent electric and magnetic dipole moments for a set of electrically small antenna geometries. Second, it develops equivalent circuit models that express the coupling paths in terms of a coupling capacitance and mutual inductances, enabling analytical investigations consistent with the FEM results. Third, it applies the near-field characterization of electrically small antennas given by the equivalent dipole moments to shielding analysis, demonstrating that the near-field of an antenna directly determines the optimal shielding material, and confirming this through simulations of shielded antenna enclosures.

To achieve these objectives, the thesis is structured as follows. \Cref{sec:dipole-theory} establishes the theoretical foundations of electric and magnetic dipole moments, their radiated fields, and the derivation of equivalent lumped reactances. \Cref{sec:guided-waves} develops the framework for electromagnetic coupling in waveguides and TEM cells, including the derivation of modal coupling coefficients, the theory of electromagnetic shielding, and methods for determining shielding effectiveness. \Cref{sec:simulations} provides a concise overview of the finite element method as implemented in HFSS. \Cref{sec:num-inv} presents the numerical investigations of the antenna and TEM cell models, covering the monopole and loop antennas as main study cases alongside three additional antenna geometries, and derives equivalent circuit models for the first two antennas. Finally, \cref{sec:shielding-sim} demonstrates the application of shielding materials in the presence of dipole moments and electrically small antennas, and \autoref{sec:conclusions} summarizes the conclusions and provides directions for future work.
